\documentclass[10pt,letterpaper]{article}

\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{left=0.75in, right=0.75in, top=0.75in, bottom=0.75in}
\renewcommand\refname{\centering Works Cited}

\def\name{Xiaoli Sun, Jaydeep Hemant Rotithor}


\begin{document}
\begin{titlepage}
\begin{center}
    \Huge
    \textbf{Project 4}
    
    \vspace{0.5in}
    \large
    CS444 - Operating Systems II\\
    
    \vspace{0.2in}
    \large
    Fall 2017\\
    
    \vspace{0.2in}
    \large
    Instructor: D. Kevin McGrath\\
    
    \vspace{0.2in}
    \textbf{Xiaoli Sun, Jaydeep Hemant Rotithor}
    
    \vspace{0.5in}
    \textbf{Abstract}\\
    \vspace{0.2in}
    
    
    \vspace{0.3in}
    \vfill
    %\Large 
    
    Nov 27, 2017

\end{center}
\end{titlepage}




\newpage
\section{The design of best fit allocation algorithm}
\subsection{Plans:}
Before implementing best fit memory allocation algorithm we need to do some research on how current slob algorithm works. The default slob algorithm is written in first fit algorithm. In the first fit algorithm, the allocator scans a list of block and choose the first sufficient block from top of memory for requested memory. This algorithm may cause page fragmentation and thus cause inefficient. Therefore we need to implement best fit algorithm to improve the efficient and reduce fragmentation. 
Our plan is that we need to find a best fitting space. To find a best fitting space, we need to look through the code first especially these two functions: slob\_page\_alloc() and slob\_alloc(). After we find the best fitting place, then we can allocate memory to that place. 

\subsection{Solutions:}


\textbf{}

\section*{Command List}



\section{Version Control}

\textbf{}

\begin{tabular}{|l|l|l|p{8cm}|} \hline


\end{tabular}

\section{Work log}

\textbf{}

\begin{tabular}{|l|p{12cm}|} \hline
Date & Summary\\ \hline
Friday, 11.03.17 & Looked over project requirements and began planning.\\ \hline
Tuesday, 11.07.17 & Upload default makefile and Kconfig under deivers/block\\ \hline
Wednesday, 11.08.17 & Get help from Internet and fixing bugs in driver file and upload new makefile and kconfig as well \\ \hline
Thursday, 11.09.17 & Adding patch file, also add some comments in the code \\ \hline
Friday, 11.10.17 &  Finished write-up and prepare to submit the assignment.\\ \hline

\end{tabular}

\section{Project questions}

\textbf{}

\textbf{1. What do you think the main point of this assignment is?}\\



\textbf{2. How did you personally approach the problem? Design decisions, algorithm, etc.}\\


\textbf{3. How did you ensure your solution was correct? Testing details, for instance.}\\



\textbf{4. What did you learn?}\\



\end{document}